\documentclass[11pt,a4paper]{article}
\usepackage[margin=2.5cm]{geometry}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{parskip}

% PJD Brand Colours
\definecolor{pjdnavy}{HTML}{0A192F}
\definecolor{pjdgold}{HTML}{FFD700}

% Section formatting
\titleformat{\section}{\large\bfseries\color{pjdnavy}}{}{0em}{}[\color{pjdgold}\titlerule]
\titleformat{\subsection}{\normalsize\bfseries\color{pjdnavy}}{}{0em}{}

% Header/Footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small\color{pjdnavy}\textbf{Paul Jeggels Designs}}
\fancyhead[R]{\small\color{pjdnavy}Ordering, Payment \& Delivery FAQ}
\fancyfoot[C]{\small\color{pjdnavy}15 Dageraad Street, Jeffreys Bay \,|\, +27 82 960 9353 \,|\, pauljeggelsdesigns.co.za}
\fancyfoot[R]{\small\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

% Q&A formatting
\newcommand{\question}[1]{\subsection*{Q: #1}}
\newcommand{\answer}{\noindent\textbf{A:} }

\begin{document}

\begin{center}
{\LARGE\bfseries\color{pjdnavy} Paul Jeggels Designs}\\[6pt]
{\Large\color{pjdnavy} Ordering, Payment \& Delivery FAQ}\\[4pt]
{\small\color{gray} Everything You Need to Know About Getting Your Board}
\end{center}

\vspace{1em}

% ─────────────────────────────────────────────────────────────────────
\section{The Ordering Process}
% ─────────────────────────────────────────────────────────────────────

\question{How do I order a custom board from Paul?}
\answer It starts with a conversation. You can:
\begin{itemize}[leftmargin=1.5em]
    \item \textbf{Call or WhatsApp}: +27 82 960 9353
    \item \textbf{Use the website}: Fill in the contact form or take the board quiz at pauljeggelsdesigns.co.za
    \item \textbf{Visit the workshop}: 15 Dageraad Street, Jeffreys Bay --- walk-ins welcome
\end{itemize}
Paul will ask about your height, weight, surfing experience, the waves you ride, and what you're looking for in a board. From that conversation, he'll recommend a shape, dimensions, and fin setup. Once you're happy with the spec, you pay a deposit and Paul gets to work.

\question{What happens during the consultation?}
\answer Paul asks the right questions --- not to fill a form, but because each answer changes the board. He'll want to know:
\begin{itemize}[leftmargin=1.5em]
    \item Your height and weight (for volume and sizing)
    \item How long you've been surfing and how often
    \item What breaks you surf most (beach break, point, reef)
    \item What you like and don't like about your current board
    \item Any specific requests (colour, artwork, fin system)
\end{itemize}
If you're local, Paul might suggest meeting at the workshop so he can show you blank options and talk through the shape in person. If you're ordering remotely, a phone call or WhatsApp chat works just as well. Paul has been doing this for over 40 years --- he knows what questions to ask.

\question{What's the step-by-step process from order to pickup?}
\answer
\begin{enumerate}[leftmargin=1.5em]
    \item \textbf{Consultation}: You and Paul discuss your surfing, body, and preferences (15--30 minutes).
    \item \textbf{Quote and deposit}: Paul gives you a price based on the board spec. You pay a 50\% deposit to confirm the order.
    \item \textbf{Shaping}: Paul shapes the blank by hand in his workshop. This is where 40+ years of experience comes in.
    \item \textbf{Glassing}: The shaped blank gets laminated with fibreglass and resin. Colour work happens at this stage.
    \item \textbf{Finishing}: Sanding, fin box installation, leash plug, and final inspection.
    \item \textbf{Collection or delivery}: Paul lets you know it's ready. You pay the balance and pick it up --- or he arranges delivery.
\end{enumerate}

\question{Can I order a board if I don't know what I want?}
\answer Absolutely --- that's what most first-time customers do. Paul's job is to figure out what you need based on who you are as a surfer. You don't need to walk in with a spec sheet. Just tell him about your surfing and he'll recommend the right board. The quiz on the website is a good starting point if you want to explore before you call.

% ─────────────────────────────────────────────────────────────────────
\section{Pricing \& Payment}
% ─────────────────────────────────────────────────────────────────────

\question{How much does a custom board cost?}
\answer Custom boards start from R5,000 and go up to R15,000+ depending on the size, type, and finish. A standard shortboard or fish is on the lower end. Longboards, heavy glass jobs, and custom artwork push the price up. Paul will give you an exact quote during the consultation --- no surprises.

\question{Do I need to pay a deposit?}
\answer Yes. A 50\% deposit is required to confirm your order and secure your spot in the shaping schedule. The remaining 50\% is due when the board is ready for collection. Paul doesn't start shaping until the deposit is received.

\question{What payment methods do you accept?}
\answer Bank transfer (EFT) is the standard method for South African customers. Paul can also accept cash on collection at the workshop. For international orders, bank transfer in ZAR is preferred --- Paul will provide his banking details. Contact him directly to discuss international payment arrangements.

\question{Can international customers order?}
\answer Yes. Paul has shaped boards for surfers from Germany, the UK, Australia, and beyond. International orders follow the same process --- consultation via phone or WhatsApp, deposit via bank transfer, and shipping arranged once the board is complete. Prices are quoted in South African Rand (ZAR), which often makes PJD boards excellent value compared to custom boards priced in Euros, Pounds, or US Dollars.

% ─────────────────────────────────────────────────────────────────────
\section{Lead Times}
% ─────────────────────────────────────────────────────────────────────

\question{How long does it take to get my board?}
\answer Typically 2--4 weeks from deposit to completion. The exact timeline depends on:
\begin{itemize}[leftmargin=1.5em]
    \item \textbf{Current workload}: If Paul has a queue of orders, your board joins the line.
    \item \textbf{Board complexity}: A standard shortboard is quicker than a longboard with custom artwork.
    \item \textbf{Blank availability}: Occasionally a specific blank needs to be ordered in.
    \item \textbf{Weather and curing}: Resin needs proper curing time, which can be affected by temperature and humidity.
\end{itemize}
Paul will give you an estimated timeline when you place your order and keep you updated if anything changes.

\question{Can I get a rush order?}
\answer Sometimes, if Paul's schedule allows it. If you're visiting J-Bay for a trip and need a board quickly, mention that upfront. Paul will do his best to accommodate, but he won't rush the quality. A board shaped in a hurry is a board shaped wrong --- and Paul doesn't do that.

% ─────────────────────────────────────────────────────────────────────
\section{Delivery \& Shipping}
% ─────────────────────────────────────────────────────────────────────

\question{Can I pick up my board from the workshop?}
\answer Yes, and it's the best option. You get to see your board in person, Paul walks you through the shape and fin setup, and you can ask any questions before you paddle out. The workshop is at 15 Dageraad Street, Jeffreys Bay --- easy to find and Paul's usually there.

\question{Do you deliver within South Africa?}
\answer Yes. Paul can arrange courier delivery anywhere in South Africa. Boards are packaged in protective wrapping for transit. Delivery cost depends on the destination and board size --- Paul will quote you when the board is ready. Common routes (to Cape Town, Durban, PE) are well-established.

\question{What about international shipping?}
\answer International shipping is possible but handled on a case-by-case basis. Boards need to be properly packed for air or sea freight, and customs/import duties are the buyer's responsibility. Paul will help arrange the logistics and provide a shipping quote. Many international customers combine their order with a surf trip to J-Bay and take the board home with them --- board bags for travel are available.

% ─────────────────────────────────────────────────────────────────────
\section{Warranty \& Aftercare}
% ─────────────────────────────────────────────────────────────────────

\question{Is there a warranty on custom boards?}
\answer Paul stands behind his craftsmanship. If there's a manufacturing defect --- delamination not caused by heat or impact, a fin box that fails under normal use, or a structural issue with the glass job --- Paul will make it right. This is a craftsmanship guarantee, not an insurance policy. Normal wear and tear, dings from surfing, and damage from misuse (leaving the board in the sun, etc.) are not covered. Paul's reputation is built on making boards that last, and he takes that seriously.

\question{Can I return or exchange a custom board?}
\answer Custom boards are made to your specifications, so returns aren't offered. The deposit is non-refundable once shaping has begun. This is standard practice for custom surfboards worldwide --- it's a one-off product built specifically for you. That said, if something isn't right with the board, talk to Paul. He wants you to be stoked, and he'll work with you to sort out any issues.

\question{What if my board gets damaged after a few months?}
\answer Bring it to Paul for a ding repair. Repairs start from R500 and most minor work is turned around in a few days. Paul and the team repair boards the same way they build them --- with proper materials and attention to detail. Your board gets the same care whether it's brand new or five years old.

% ─────────────────────────────────────────────────────────────────────
\section{Second-Hand Boards}
% ─────────────────────────────────────────────────────────────────────

\question{Does Paul sell second-hand boards?}
\answer Yes. Paul regularly has a selection of second-hand boards in the workshop --- boards that were shaped by him, ridden a few times, and traded in or returned. Every second-hand board is inspected and repaired before it goes on sale. Prices vary depending on the board, but they're always well below the cost of a new custom shape.

\question{How do I know if a second-hand board is in good condition?}
\answer Paul inspects every board before listing it. He checks for water damage, delamination, structural cracks, and fin box condition. If a board needs work, he fixes it first. When you buy a second-hand board from PJD, you're getting a board that's been vetted by the same person who shaped it. You won't find that at a second-hand surf shop.

\question{Can I trade in my old PJD board?}
\answer Talk to Paul. If you've got a PJD board you've outgrown or want to upgrade from, he may take it as a trade-in towards your new custom order. The value depends on the board's condition and age. It's a good way to keep the cost down on your next shape.

% ─────────────────────────────────────────────────────────────────────
\section{Reordering}
% ─────────────────────────────────────────────────────────────────────

\question{I love my board. Can I get the exact same one again?}
\answer Yes. Paul keeps records of the boards he shapes --- dimensions, rocker, foil, fin setup, everything. If you want an identical board (or a slight variation), he can reproduce it. Many of Paul's long-term customers are on their third, fourth, or fifth board --- each one refined from the last based on feedback. That's the advantage of a relationship with your shaper.

\question{Can Paul adjust my next board based on how the last one rides?}
\answer Absolutely, and this is where custom shaping really shines. Tell Paul what you love about your current board and what you'd change. A little more volume? Slightly narrower tail? Different fin setup? He'll take that feedback and dial in the next shape. Over time, your boards get closer and closer to your perfect ride. That's the PJD experience --- it's not a one-off transaction, it's an ongoing relationship.

\vfill
\begin{center}
\small\color{gray}
Paul Jeggels Designs --- 15 Dageraad Street, Jeffreys Bay, South Africa\\
Phone: +27 82 960 9353 --- Hand-shaped surfboards since the 1980s
\end{center}

\end{document}
